---
title: "P8105_hw1_REN XIN"
output: github_document
date: "2022-09-23"
---
```{r}
library(tidyverse)
library(readxl)
library(readr)
library(dplyr)
```


Problem1
```{r}
trans_ent = 
  read_excel(
    "NYC_Transit_Subway_Entrance_And_Exit_Data.xlsx")
col_types = cols(Route8 = "c", Route9 = "c", Route10 = "c", Route11 = "c")
trans_ent=janitor::clean_names(trans_ent)
data_c=select(trans_ent,line,station_name,station_latitude,station_longitude,route1:route11,entry,vending,entrance_type,ada) %>% 
  mutate(entry = ifelse(entry == "YES", TRUE, FALSE))
```
```{r}
trans_ent %>% 
  select(station_name, line) %>% 
  distinct
```
```{r}
trans_ent %>% 
  filter(ada == TRUE) %>% 
  select(station_name, line) %>% 
  distinct
```
```{r}
trans_ent %>% 
  filter(vending == "NO") %>% 
  pull(entry) 
```
```{r}
trans_ent=mutate(trans_ent,route8=as.character(route8))
trans_ent=mutate(trans_ent,route9=as.character(route9))
trans_ent=mutate(trans_ent,route10=as.character(route10))
trans_ent=mutate(trans_ent,route11=as.character(route11))
trans_ent %>% 
  pivot_longer(
    route1:route11,
    names_to = "route_num",
    values_to = "route") %>% 
  filter(route == "A") %>% 
  select(station_name, line) %>% 
  distinct

trans_ent %>% 
  pivot_longer(
    route1:route11,
    names_to = "route_num",
    values_to = "route") %>% 
  filter(route == "A", ada == TRUE) %>% 
  select(station_name, line) %>% 
  distinct
```


Problem2
```{r}
Trash_WCD_df = 
    read_excel("Trash Wheel Collection Data (1).xlsx",sheet = "Mr. Trash Wheel") 
Trash_WCD_df=janitor::clean_names(Trash_WCD_df) 
Trash_WCD_df%>%     
drop_na(dumpster) %>% 
    mutate(sports_balls = as.integer(round(sports_balls)),)
Trash_WCD_df
```
```{r}
Professor_TW_df = 
    read_excel("Trash Wheel Collection Data (1).xlsx",sheet = "Professor Trash Wheel") 
Professor_TW_df=janitor::clean_names(Professor_TW_df) 
Professor_TW_df%>% 
drop_na(dumpster) %>% 
    mutate(
      dumpster=as.character(dumpster)
    )
Professor_TW_df
```


```{r}
Trash_WCD_df=Trash_WCD_df[,-c(15:16)]
Trash_WCD_df=mutate(Trash_WCD_df,name=as.character("Mr. Trash Wheel"))
Professor_TW_df=mutate(Professor_TW_df,name=as.character("Professor Trash Wheel"))
Trash_WCD_df=mutate(Trash_WCD_df,year=as.double(year))
Trash_Professor= bind_rows(Trash_WCD_df,Professor_TW_df)
Trash_Professor
```
```{r}
TW_trash=sum(Professor_TW_df$weight_tons[1:94])
filter_TWCD=filter(Trash_WCD_df,year==2020)
TN_sport=sum(filter_TWCD$sports_balls)
TW_trash
TN_sport
```

Description：
   According to the data, the key variables are month,year,date weights_tons,and so on, which totally has 14 columns and 95 entries.the total weight of trash collected by Professor Trash Wheel is  ```sum(Professor_TW_df$weight_tons[1:94])```, and the total  number of sports balls collected by Mr. Trash Wheel in 2020 is ```=sum(filter_TWCD$sports_balls)```, but before we sum that, we need to select the tumber of data at 2020,and then do the sum step.

Problem3

```{r}
Une=read_csv("unemployment.csv")
pols_month=read_csv("pols-month.csv")
S=read_csv("snp.csv")
Une
pols_month
S
```

```{r}
pols_month = separate(pols_month,col=mon, into= c('year','month','day'))
pols_month = janitor::clean_names(pols_month)
pols_month=pols_month%>%
  mutate(month = recode(month, "01" = "Jan", "02" = "Feb", "03"="Mar", "04"="Apr","05"="May","06"="Jun", "07"="Jul", "08"="Aug","09"="Sep","10"="Oct","11"="Nov", "12"="Dec")
)
pols_month=pols_month%>%
  mutate(president=ifelse(prez_gop==1, "prez_gop",ifelse(prez_gop==0,"prez_dem","gop_2") ))
pols_month
```


```{r}
pols_month=select(pols_month, -day,-prez_gop,-prez_dem)
pols_month
```


```{r}
S = separate(S,date, into= c("month","day",'year'),sep= "/")
S=mutate(S, month = recode(month, "1" = "Jan", "2" = "Feb", "3"="Mar", "4"="Apr","5"="May","6"="Jun", "7"="Jul", "8"="Aug","9"="Sep","10"="Oct","11"="Nov", "12"="Dec")
)
```

```{r}
S=mutate(S,year=as.integer(year))
S=mutate(S,year=as.integer(year))
S
```

```{r}
A_df=pivot_longer(Une,Jan:Dec,names_to="month",values_to="amount")
A_df=select(A_df, year=Year,month,amount)
A_df=mutate(A_df,year=as.integer(year))
A_df=mutate(A_df,month=as.integer(month))
A_df
S=mutate(S, year = ifelse(year<20,year + 2000,year + 1900)
)
S=arrange(S,year,month)
S=relocate(S, year, month,close)
S = mutate(S,year=as.character(year))
```
```{r}
unemploynment = janitor::clean_names(Une)
unemploynment = pivot_longer(unemploynment, jan:dec, names_to = "month", values_to = "amount")
unemploynment = mutate(unemploynment,month = recode(month, 'jan'='Jan', 'feb'='Feb', 'mar'= 'Mar', 'apl'= 'Apr', 'jun' = 'Jun', 'jul'= 'Jul', 'aug'= 'Aug', 'sep' = 'Sep', 'oct'= 'Oct', 'nov' = 'Nov', 'dec' = 'Dec'))
S=select(S,-day)
pols_month=mutate(pols_month,year=as.double(year))
S=mutate(S,year=as.double(year))
```



```{r}
join_datasets = left_join(pols_month,S)
```

```{r}
join_datasets = left_join(join_datasets,unemploynment)
join_datasets
```
Description:
1.After deal with unemployment data, which total has 816 entries, 3 columns,especially( year,month,amount),the dimension is 816x3. The range of years is from 1948 to 2015.
2.After deal with pols_month data, which total has 822 entries, 9 columns,especially( year,month,gov_gop,sen_gop,rep_gop,gov_dem,sen_dem,rep_dem,president),the dimension is 822x9. The range of years is from 1947 to 2015.
3.After deal with snp data, which total has 787 entries, 3 columns,especially( year,month,close),the dimension is 787x3. The range of years is from 1950 to 2015.

