---
title: "P8105_hw1_REN XIN"
output: github_document
date: "2022-09-23"
---
```{r}
library(tidyverse)
```


Problem 1:

```{r}
library(palmerpenguins)
data("penguins", package = "palmerpenguins")
```
```{r}
penguins <- na.omit(penguins)
```

```{r}
nrow(penguins)
ncol(penguins)
mean(pull(penguins,flipper_length_mm))
```
description:
1. The data(penguins) has 344rows(one row of NA) and 8 columns.
2. The flipper length is `r mean(pull(penguins,flipper_length_mm))`
3. The data including 8 columns, which are species, island, bill_length_mm,bill_depth_mm,flipper_length_mm,body_mass_g, sex and year.
```{r}
scatterplot_df=
  tibble( 
    bill_length_mm = pull(penguins,bill_length_mm),
    flipper_length_mm = pull(penguins,flipper_length_mm)
  )
ggplot(scatterplot_df, aes(x= bill_length_mm,y= flipper_length_mm))+geom_point (aes(color=pull(penguins, species)))
ggsave("scatterplot of p8105_hw1_RX.pdf")
```

Problem 2:

```{r}
df=tibble(
   norm_nb = rnorm(10),
   norm_logical = norm_nb>0,
   norm_character = as.character(norm_nb),
   df_factor=factor(c("10","15","20","10","15","20","10","15","20","10"),levels = c("10","15","20"))
)
```

The norm_nb's mean is `r mean(pull(df,norm_nb))`
The norm_logical's mean is `r mean(pull(df,norm_logical))`
The norm_character's mean is `r mean(pull(df,norm_character))`
The df_factor's mean is `r mean(pull(df,df_factor))`

```{r}
as.numeric(df$norm_character)
as.numeric(df$df_factor)
```

Now,The norm_character’s mean is NA The df_factor’s mean is NA,So,
The norm_character's mean is `r mean(as.numeric(df$norm_character))`
The df_factor's mean is `r mean(as.numeric(df$df_factor))`


